Supplementary material

### 2022-03-28 analysis/supplementary-materials/supplementary.Rmd
Minor edits
Updates to text and figure

Stone Age sites for which no spatial data was readily available are Frebergsvik A--C [@mikkelsen1975], Nedre Holtan [@sjursjeike], Rugtvedt [@odgaard1994], Tangen [@glorstad2005], and Torsrød [@østmo1975]. These sites are therefore not included in the analysis. Furthermore, @nielsen2021 has recently interpreted features from the otherwise younger sites Bratsberg and Larønningen as possibly related to farming activity in the Early Neolithic. However, given the limited number of features, the lack of any artefacts directly related to these, and the therefore somewhat speculative nature of this suggestion, the sites are kept out of the analysis here.

@@

The site limit for Auve was drawn manually based on the description in the publication of the site and the site geometry available in the database Askeladden. The area to the has reportedly been affected by land-slides, but the extent of this is difficult to ascertain based on maps of the area. As the simulation results appear reasonable [see also map in @ostmo2008, fig.142], nothing was done to try to correct for this.

@@

The radiocarbon date to the Stone Age is not related to the site inventory, which is distinctly Early Mesolithic in character [@nyland2012b].

>>>>

Stone Age sites for which no spatial data was readily available are Frebergsvik A--C [@mikkelsen1975], Nedre Holtan [@sjursjeike], Rugtvedt [@odgaard1994], Tangen [@glorstad2005], and Torsrød [@østmo1975]. These sites are therefore not included in the analysis. Furthermore, @nielsen2021b has recently interpreted features from the otherwise younger sites Bratsberg and Larønningen as possibly related to farming activity in the Early Neolithic. However, given the limited number of features, the lack of any artefacts directly related to these, and the therefore somewhat speculative nature of this suggestion, the sites are kept out of the analysis here.

@@

The site limit for Auve was drawn manually based on the description in the publication of the site and the site geometry available in the database Askeladden. The site is located in and around an intersection of the road, parts of the area has been levelled and farmed, and an area to north-west of the site has reportedly been affected by land-slides [@ostmo2008, 16--29] , but the extent of this is difficult to ascertain based on maps of the area. As the simulation results appear reasonable [see also map in @ostmo2008, fig.142], nothing was done to try to correct for these factors.

@@

The radiocarbon date to the Stone Age is not related to the site inventory at Bakke, which is distinctly Early Mesolithic in character [@nyland2012b].
